\cvsection{Experience}
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Web Designer (Freelance)} % Job title
    {PT. Wijawa Kusuma Sukses} % Organization
    {Bekasi, Indonesia} % Location
    {Apr. 2017 - Mar. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Design a web application with Content Management System (CMS) that can support and help the administrative supervisor.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Researcher (Internship Program)} % Job title
    {Indonesian Institute of Sciences} % Organization
    {Bogor, Indonesia} % Location
    {May - Aug. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Researched Grid Refinement algorithms to improve accuracy of blood flow simulation with Navier-Stokes equations and Lattice Boltzmann method}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Parallel Computing Division} % Job title
    {High Performance Computing Research Group Telkom University} % Organization
    {Bandung, Indonesia} % Location
    {Jan. 2017 - May. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Researched parallel algorithms using OpenMP to improve performance and reduce time complexity that implements in Images Overlay with Noise Reduction and Contrast Enhancement.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Practicum Assistant} % Job title
    {Informatics Laboratory of Telkom University} % Organization
    {Bandung, Indonesia} % Location
    {Jan. 2016 - Apr. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Teach and assist students in practice as needed to establish programming skills and logical analysis.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {IT Support (Internship Program)} % Job title
    {PT. Pos Indonesia} % Organization
    {Lamongan, Indonesia} % Location
    {May 2016 - Jul. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Improving the functionality of the software to be more optimal and troubleshooting hardware and software.}
      \end{cvitems}
    }


%---------------------------------------------------------
\end{cventries}
